Recovery of deleted deep sequencing data sheds more light on the early Wuhan SARS-CoV-2 epidemic

### 2021-06-18 paper/paper.tex
methods on bat CoVs

>>>>

\subsection{Bat coronavirus outgroup sequences}
For analyses that involved comparisons to SARS-CoV-2's bat coronavirus relatives~\citep{lytras2021exploring}, the bat coronavirus sequences were manually downloaded from GISAID~\citep{shu2017gisaid}.
The sequences used were RaTG13~\citep{zhou2020pneumonia}, RmYN02~\citep{zhou2020novel}, and RpYN06~\citep{zhou2021identification}---although the multiple sequence alignment of these viruses to SARS-CoV-2 also contains PrC31~\citep{li2021novel}, which was not used in the final analyses as it more diverged from SARS-CoV-2 than the other three bat coronaviruses at a whole-genome level.
The GISAID accessions for these sequences are listed at \url{https://github.com/jbloom/SARS-CoV-2_PRJNA612766/blob/main/data/comparator_genomes_gisaid/accessions.txt}, and  a table acknowledging the labs and authors is at \url{https://github.com/jbloom/SARS-CoV-2_PRJNA612766/blob/main/data/comparator_genomes_gisaid/acknowledgments.csv}.
Sites in SARS-CoV-2 were mapped to their corresponding nucleotide identities in the bat coronavirus outgroups via a multiple sequence alignment of proCoV2 to the bat coronaviruses generated using \texttt{mafft}~\citep{katoh2013mafft}.

\subsection{Curation and analysis of early SARS-CoV-2 sequences from GISAID}
I manually
